A histogram of the total number of steps each day:

```{r, cache = TRUE}
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url, destfile = "activity.zip", method = "curl")
unzip("activity.zip", "activity.csv")
fitbit <- read.csv("activity.csv", header = TRUE)
**need to sum by day**hist(fitbit$steps)
```

Also, calculating the mean and median steps:  
```{r stats, cache = TRUE}
mean(fitbit$steps, na.rm = TRUE)
median(fitbit$steps, na.rm = TRUE)
```

In addition, we want to look at average of steps per 5 minute interval:

```{r time, cache = TRUE}
steps_by_interval <- aggregate(steps ~ interval, data = fitbit, mean, na.rm = TRUE)
plot(steps_by_interval$interval, steps_by_interval$steps, type = "l")
```
```{r, cache = TRUE}
maxid <- which.max(steps_by_interval$steps)
maxinterval <- steps_by_interval$interval[maxid]
```
Maximum steps by interval occurs in `r maxinterval` interval.

```{r, cache = TRUE}
missing <- sum(is.na(fitbit$steps))
```

Many values are missing in this data set. Total number of rows with missing values is: `r missing`.

This time, we'll be replacing all the missing data with the average data from that interval across the rest of the days. Looking at the new histogram of steps...

```{r, cache = TRUE}
fitbit2 <- data.frame(fitbit)
fitbit2[is.na(fitbit2)] <- steps_by_interval$steps 
hist(fitbit2$steps)
```

And the new mean and median of the data with the missing data filled in:

```{r}
mean(fitbit2$steps)
median(fitbit2$steps)
```

We also want to know what's different between the weekdays and weekends.

```{r}
fitbit2$date2 <- as.Date(fitbit2$date, format = "%Y-%m-%d")
fitbit2$weekday <- weekdays(fitbit2$date2)
fitbit2$weekday_factor <- ifelse(fitbit2$weekday %in% c("Saturday", "Sunday"), "Weekend", "Weekday")
fitbit2$weekday_factor <- as.factor(fitbit2$weekday_factor)
steps_by_interval2 <- aggregate(steps ~ interval, data = fitbit2, mean)
fitbit2$avg_by_interval <- rep(steps_by_interval2$steps, 61)
library(ggplot2)

qplot(x = interval, y = avg_by_interval, data = fitbit2, geom = "line", facets = weekday_factor ~ .)
